### 2024-01-16 documentation/thesis/thesis_document.tex
more thesis
v3

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}
\caption{Example hallbach ring magnet with cutouts for eight cubical
permanent magnets
\label{Example_hallbach_ring_magnet_with_cutouts_for_eight_cubical_permanent_magnets.png}}
\end{figure}

@@

\begin{itemize}
\item
  \textbf{Material}

  The magnetic properties of a material influence the generated field
  strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}

  The orientation of the magnetic moments in the material influences the
  field strength. A higher magnetization leads to a stronger field
  strength.
\item
  \textbf{Temperature}

  Temperature can influence the magnetic properties of a material. The
  magnetization of some materials decreases with increasing temperature.
\item
  \textbf{Manufacturing process}

  The manufacturing process can influence the magnetic properties of the
  material. This is dependent on the purity of the starting materials
  used and the processing methods. There may also be deviations in field
  strength if different magnets from different production batches are
  compared.
\end{itemize}

@@

\begin{itemize}
\item
  Chapter \ref{state-of-the-art}. \textbf{State of the Art} describes
  the current state of technology and forms the basis for further
  development. Existing measurement methods and findings are shown here
  in order to define the context for the current project.
\item
  Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
  which the project is to be used. They illustrate the practical
  scenarios and define how the product can be used in the real world.
  This is crucial for understanding the needs of the target group and
  designing the end result accordingly.
\item
  Chapter \ref{unified-sensor}. \textbf{Unified Sensor} refers to the
  integration of different sensors into a standardised solution. This
  enables simple data acquisition and serves as a basic hardware system
  on which the subsequent data processing library can be applied.
\item
  Chapter \ref{software-readout-framework}. \textbf{Software Readout
  Framework} describes the implementation of the data readout framework.
  This includes an explanation of the various modules and specific
  application examples.
\item
  Chapter \ref{usability-improvements}. \textbf{Usability Improvements}
  refers to additional activities to improve user-friendliness. This
  includes the optimisation of interfaces, interactions and processes to
  ensure intuitive and efficient use of the product. This also includes
  the documentation of code and the distribution of the source code as a
  package to users.
\item
  Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
  review and assessment of the overall system. This includes the
  demonstration of the implemented capabilities of the overall system
  against the previously defined usecases.
\end{itemize}

@@

This ensures broad applicability in different scenarios. Another goal is
reproducibility to ensure consistent results. Easy communication with
standard PC hardware maximises the user-friendliness of the interface.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_mechanical_3D_printed_structure.png}
\caption{1D sensor mechanical 3D printed structure
\label{1D_sensor_mechanical_3D_printed_structure.png}}
\end{figure}

@@

The following figure
\ref{1D_sensor_mechanical_3D_printed_structure.png}, shows a sectional
view of the \gls{cad} drawing of the 1D-Single sensor
\ref{d-single-sensor}.

@@

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_strucutre.png}
\caption{Unified sensor firmware simplified program strucutre
\label{Unified_sensor_firmware_simplified_program_strucutre.png}}
\end{figure}

@@

The flow chart
\ref{Unified_sensor_firmware_simplified_program_strucutre.png} shows the
start process and the subsequent main loop for processing the user
commands and sensor results. When the microcontroller is started, the
software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces.

@@

After the setup process is complete, the system switches to an infinite
loop, which processes several possible actions. One task is, to react to
user commands which can be sent to the system by the user via the
integrated \gls{cli}. All sensors are read out via a timer interval set
in the setup procedure and their values are stored in a ringbuffer. Ring
buffer offers efficient data management in limited memory. Its cyclic
structure enables continuous overwriting of older data, saves memory
space and facilitates seamless processing of real-time data.

@@

\hypertarget{communication-interface}{%
\subsection{Communication interface}\label{communication-interface}}

@@

\hypertarget{example-sensors}{%
\section{Example sensors}\label{example-sensors}}

@@

Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
measurement range of total \passthrough{\lstinline!6uT!}, even small
coin sized neodymium magnets already saturates the sensor. It is
possible to mount 3D printed spacers over the sensor to increase the
distance between the magnet and the sensor and thus also measure these
magnets.

@@

\hypertarget{integration-of-an-industry-teslameter}{%
\subsection{Integration of an industry
teslameter}\label{integration-of-an-industry-teslameter}}

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of \passthrough{\lstinline!0-3T!} with
a resolution of \passthrough{\lstinline!0.1mT!}. It offers an
\passthrough{\lstinline!RS232!} interface with a documented protocol
\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the Unified Sensor ecosystem using a separate interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the Unified Sensor
firmware offers.

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \passthrough{\lstinline!RS232!} interface. As with the
other sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter.

The Teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

\hypertarget{software-readout-framework}{%
\chapter{Software readout framework}\label{software-readout-framework}}

@@

@@

The \passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner} opensource project, can generate basic
\gls{cad} drawings for \gls{mri} magnets in a Hallbach configuration. To
do this, the number of magnets and additional parameters for the
properties of the \gls{cad} model to be created are passed to the
function provided as input parameters using a \gls{json} file. The
result is then an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
based 3D model of the magnet holder.

As a result, there are two projects which are both suitable for the task
of optimizing and creating Hallbach magnets for \gls{mri} applications.
However, their data structures are not compatible with each other.
However, they are executed manually one after the other in order to
obtain a final result.

The library created is intended to solve one problem by providing
standardized and flexible data structures for use with this form of
magnetic field data. On the other hand, by separating the processing
pipeline into defined sub-steps, it should be possible to make
individual modules and as a result functionalities interchangeable by
the user.

@@

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the
\passthrough{\lstinline!HalbachOptimisation!}
\cite{HalbachOptimisation} project, the function signature of the
start function must be changed. This receives the result of the previous
step, in this case the generated magnet data. By optionally setting meta
data in the universal bilbiothekt data type, constants can be replaced
in the analysis function and made dynamically configurable. The return
result also corresponds to this data type so that subsequent steps are
compatible and contains the magnet data with modified position and
rotation data.

@@

After these customization steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly.

@@

In order to realise the concept of user interaction points, the library
was divided into different modules. These can be divided into two main
categories:

\begin{itemize}
\tightlist
\item
  Core - All modules related to measurement data management
\item
  Extensions - Contains modules for visualizations, hardware sensor
  access
\end{itemize}

@@

\hypertarget{storage-and-datamanagement}{%
\subsubsection{Storage and
Datamanagement}\label{storage-and-datamanagement}}

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!additional\_data!} - Additional user-defined
  metadata
\item
  \passthrough{\lstinline!data!} - Measured values with value and
  measured value \gls{uuid}
\item
  \passthrough{\lstinline!measurement\_config!} - Information about the
  sensor used for measurement
\end{itemize}

@@

Since there are popular data processing frameworks such as
\passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
program for mathematical calculations, Matlab are often used, the
library also supports export formats for these systems.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!.dump()!} - \gls{json}
\item
  \passthrough{\lstinline!.to\_numpy\_matrix()!} -
  \passthrough{\lstinline!Numpy!}-Array of
  \passthrough{\lstinline!data!} object with different options
\item
  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
  measurement values and temperatures
\end{itemize}

Currently, data re-import of an exported measurement is only supported
via the \gls{json} format, as an export using the other options
(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!Matlab!})loses
data during the export procedure. \}

@@

The extention modules build on the core modules and offer the user
additional basic functionalities. These include functions for data
acquisition, visualization and analysis.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!std\_deviation!} - standard deviation
\item
  \passthrough{\lstinline!mean!} - mean value
\item
  \passthrough{\lstinline!variance!} - variance
\item
  \passthrough{\lstinline!center\_of\_gravity!} - center of gravity
\item
  \passthrough{\lstinline!binning!} - distribution of a sample by means
  of a histogram
\item
  \passthrough{\lstinline!k-nearest!} - k-nearest neighbors
\end{itemize}

@@

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the
\passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#2!}
can acces the proxy running on
\passthrough{\lstinline!remote!}\gls{pc}\passthrough{\lstinline!\#1!}.

@@

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.

@@

\hypertarget{merging-the-sensor-capabilities}{%
\subsubsection{Merging the sensor
capabilities}\label{merging-the-sensor-capabilities}}

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarized (see
Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
the host when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command
is received over network.

@@

\hypertarget{dynamic-extension-of-the-available-network-proxy-commands}{%
\subsubsection{Dynamic extension of the available network proxy
commands}\label{dynamic-extension-of-the-available-network-proxy-commands}}

@@

For commands where there are several entries for
\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
\ref{Sensor_capabilities_merging.csv}, there are two possible approaches
to how the command is processed:

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!readsensor <axis> <sensor number>!}-\textgreater{}
  \passthrough{\lstinline!readsensor <axis> <ID>!}
\item
  \passthrough{\lstinline!opmode!}-\textgreater{}
  \passthrough{\lstinline!opmode <ID>!}
\end{itemize}

@@

\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of an measurement}, label=lst:mrpexample_hal]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
## LISTS LOCAL CONNECTED OR NETWORK SENSORS
system_ports = MRPHalSerialPortInformation.list_sensors()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path = MRPHalSerialPortInformation("UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

@@

@@

This final example shows the use of the MRP Visualisation module, which
provides general functions for visualising measurements. This makes it
possible to visually assess the results of a measurement. This is
particularly helpful for full-sphere measurements recorded with the
\passthrough{\lstinline!3D: Fullsphere!} \ref{d-fullsphere} sensor. The
sub-module \passthrough{\lstinline!MRPPolarVisualisation!} is specially
designed for these. The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement.

It is also possible to export the data from the MRPAnalysis module
graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
modules are used here. The following example
\ref{lst:mrpexample_visualisation} shows the usage of both modules.

\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a fullsphere to an image file}, label=lst:mrpexample_visualisation]
from MRP import MRPPolarVisualization
# CREATE MRPPolarVisualization INSTANCE
## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA WERE MODIFIED
visu = MRPPolarVisualization.MRPPolarVisualization(reading)
# 2D PLOT INTO A WINDOW
visu.plot2d_top(None)
visu.plot2d_side(None)
# 3D PLOT TO FILE
visu.plot3d(os.path.join('./plot3d_3d.png'))

# PLOT ANALYSIS RESULTS
from MRP import MRPDataVisualization
MRPDataVisualization.MRPDataVisualization.plot_error([reading_a, reading_b, reading_c])
\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
\caption{Generated hallbach array with generated cutouts for eight
magnets
\label{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
\end{figure}

The following example code \ref{lst:mrpexample_hallbach}, shows how a
simple hallbach magnetic ring can be generated.

This can then be used to construct a Halbach ring magnet (see chapter
\ref{Charakterisation of Permanent Magnets}) for a low-field \gls{mri}.

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD} file, which
contains the module generated. After computing the model using the
\passthrough{\lstinline!OpenSCAD!} \gls{cli} utility, the following
model rendering
\ref{Generated_hallbach_array_with_generated_cutouts_for_eight_magnets.png}
can be generated.

\hypertarget{usability-improvements}{%
\chapter{Usability improvements}\label{usability-improvements}}

@@

\begin{itemize}
\tightlist
\item
  Detection of connected sensors
\item
  Configuration of measurement series
\item
  Recording of measured values from stored measurement series
\item
  Simple commands for checking recorded measurement series and their
  data.
\end{itemize}

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again using the
\passthrough{\lstinline!MRPReading!} module and processed further. The
following bash code \ref{lst:mrpcli_config_run} shows the setup
procedure in detail:

@@

\hypertarget{programmable-data-processing-pipeline}{%
\section{Programmable data processing
pipeline}\label{programmable-data-processing-pipeline}}

@@

\begin{itemize}
\tightlist
\item
  Import the measurements
\item
  Determine sensor bias value from imported measurements using a
  reference measurement
\item
  Apply linear temperature compensation
\item
  Export the modified measurements
\item
  Create a graphical plot of all measurements with standard deviation
\end{itemize}

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.
The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} makro as input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}).

>>>>

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems measured between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

@@

\%\%Example\_hallbach\_ring\_magnet\_with\_cutouts\_for\_eight\_cubical\_permanent\_magnets.png\%\%

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
\end{itemize}

@@

Chapter \ref{usecases}. \textbf{Usecases} are the application cases in
which the project is to be used. They illustrate the practical scenarios
and define how the product can be used in the real world. This is
crucial for understanding the needs of the target group and designing
the end result accordingly.

Chapter \ref{unified-sensor}. \textbf{Unified Sensor} refers to the
integration of different sensors into a standardised solution. This
enables simple data acquisition and serves as a basic hardware system on
which the subsequent data processing library can be applied.

Chapter \ref{software-readout-framework}. \textbf{Software Readout
Framework} describes the implementation of the data readout framework.
This includes an explanation of the various modules and specific
application examples.

Chapter \ref{usability-improvements}. \textbf{Usability Improvements}
refers to additional activities to improve user-friendliness. This
includes the optimisation of interfaces, interactions and processes to
ensure intuitive and efficient use of the product. This also includes
the documentation of code and the distribution of the source code as a
package to users.

Chapter \ref{evaluation}. \textbf{Evaluation} comprises the systematic
review and assessment of the overall system. This includes the
demonstration of the implemented capabilities of the overall system
against the previously defined usecases.

@@

This ensures a wide range of applications in different scenarios.
Another goal is reproducibility to ensure uniform results, which as a
result reduces the susceptibility to errors. Easy communication with
standard \gls{pc} hardware, which offers a variety of common interface
options, maximizes the user-friendliness.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}
\caption{Mechanical components for the 1D sensor using 3D printed parts
\label{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}}
\end{figure}

@@

The following figure
\ref{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png},
shows a sectional view of the \gls{cad} drawing of the 1D-Single sensor
\ref{d-single-sensor}.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_structure.png}
\caption{Unified sensor firmware simplified program structure
\label{Unified_sensor_firmware_simplified_program_structure.png}}
\end{figure}

@@

@@

The flow chart
\ref{Unified_sensor_firmware_simplified_program_structure.png} shows the
start process and the subsequent main loop for processing the user
commands and sensor results. When the microcontroller is started, the
software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces.

@@

After execution of the setup routine is completed, the system switches
to an infinite loop, which processes several possible actions. One task
is, to react to user commands which can be sent to the system by the
user via the integrated \gls{cli}. All sensors are read out via a timer
interval set in the setup procedure and their values are stored in a
ringbuffer. Ring buffer offers efficient data management in limited
memory. Its cyclic structure enables continuous overwriting of older
data, saves memory space and facilitates seamless processing of
real-time data.

@@

\hypertarget{communication-interface}{%
\subsection{Communication Interface}\label{communication-interface}}

@@

\hypertarget{example-sensors}{%
\section{Example Sensors}\label{example-sensors}}

@@

Since the \passthrough{\lstinline!MMC5603NJ!} only has limited
measurement range of total 6uT, even small coin sized neodymium magnets
already saturates the sensor. It is possible to mount 3D printed spacers
over the sensor to increase the distance between the magnet and the
sensor and thus also measure these magnets.

@@

\hypertarget{integration-of-an-industry-teslameter}{%
\subsection{Integration of an
Industry-Teslameter}\label{integration-of-an-industry-teslameter}}

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. A temperature-compensated
\passthrough{\lstinline!Voltcraft GM-70!} telsameter
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png} is
used, which has a measuring range of 0T to 3T with a resolution of
0.1mT. It offers an RS232 interface with a documented protocol
\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a \gls{pc}.

This connectivity makes it possible to make the device compatible with
the unified sensor ecosystem using a separate interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the unified sensor
firmware offers.

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical RS232 interface. As with the other sensors, this
interface consists of your \passthrough{\lstinline!Raspberry-Pi Pico!}
with an additional level shifter.

The teslameter is connected to the microcontroller using two free
\gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

@@

\hypertarget{software-readout-framework}{%
\chapter{Software Readout Framework}\label{software-readout-framework}}

@@

\newpage

@@

The \passthrough{\lstinline!HalbachMRIDesigner!}
\cite{HalbachMRIDesigner} opensource project, can generate basic
\gls{cad} drawings for \gls{mri} magnets in a Hallbach configuration. To
do this, the number of magnets and additional parameters for the
properties of the \gls{cad} model to be created are passed to the
function provided as input parameters using a \gls{json} file. The
result is an \passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD}
based 3D model of the magnet holder.

As a result, there are two projects which are both suitable for the task
of optimizing and creating Hallbach magnets for \gls{mri} applications.
The data structures are not compatible with each other. However, they
are executed manually one after the other to obtain a final result with
manual data conversation.

The library created is intended to solve one problem by providing
standardized and flexible data structures for use with this form of
magnetic field data. By separating the processing pipeline into defined
sub-steps, it should be possible to make individual modules and as a
result functionalities interchangeable by the user.

@@

Next, the user creates his own analysis step in order to be able to call
up its functions. In the case of the
\passthrough{\lstinline!HalbachOptimisation!}
\cite{HalbachOptimisation} project, the function signature of the
start function must be changed. This receives the result of the previous
step, in this case the generated magnet data. By optionally setting meta
data in the universal library data type, constants can be replaced in
the analysis function and made dynamically configurable. The return
result also corresponds to this data type so that subsequent steps are
compatible and contains the magnet data with modified position and
rotation data.

@@

After these customisation steps, it is possible to execute both projects
one after the other and all required configuration parameters are
contained in the data structure looped through the individual steps as
meta data. This also maps the functionality of a project file, which can
be executed or passed on repeatedly.

@@

In order to realise the concept of user interaction points, the library
was divided into different modules. These modules can be divided into
two main categories:

\begin{itemize}
\tightlist
\item
  Core - All modules related to measurement data management
\item
  Extensions - Contains modules for visualisations, hardware sensor
  access
\end{itemize}

@@

\hypertarget{storage-and-datamanagement}{%
\subsection{Storage and
Datamanagement}\label{storage-and-datamanagement}}

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!additional\_data!} - Additional user-defined
  metadata
\item
  \passthrough{\lstinline!data!} - Datapoint storage consists of
  measured value, \gls{uuid} and temperature, among other parameters
\item
  \passthrough{\lstinline!measurement\_config!} - Information about the
  sensor used for measurement
\end{itemize}

@@

Since there are popular data processing frameworks such as
\passthrough{\lstinline!Numpy!} \cite{harris2020array}, or the
program for mathematical calculations, \passthrough{\lstinline!MATLAB!}
are often used, the library also supports export formats for these
systems.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!.dump()!} - \gls{json}
\item
  \passthrough{\lstinline!.to\_numpy\_matrix()!} -
  \passthrough{\lstinline!Numpy!}-Array of
  \passthrough{\lstinline!data!} object with different options
\item
  \passthrough{\lstinline!.dump\_savemat()!} -
  \passthrough{\lstinline!MATLAB!} mat-file with measurement values and
  temperatures
\end{itemize}

Currently, data re-import of an exported measurement is only supported
via the \gls{json} format, as an export using the other options
(\passthrough{\lstinline!Numpy!}, \passthrough{\lstinline!MATLAB!})loses
data during the export procedure.

@@

The extention modules build on the core modules and offer the user
additional basic functionalities. These include functions for data
acquisition, visualisation and analysis.

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!std\_deviation!} - Standard deviation
\item
  \passthrough{\lstinline!mean!} - Mean value
\item
  \passthrough{\lstinline!variance!} - Variance
\item
  \passthrough{\lstinline!center\_of\_gravity!} - Center of gravity
\item
  \passthrough{\lstinline!binning!} - Distribution of a sample by means
  of a histogram
\item
  \passthrough{\lstinline!k-nearest!} - K-nearest neighbors
\end{itemize}

@@

The figure \ref{mrp_proxy_multi.png} shows the modified
\passthrough{\lstinline!multi-proxy - multi-sensor!} topology. Here,
both proxy instances do not communicate directly with the
\passthrough{\lstinline!control!} \gls{pc}, but the proxy instance
\passthrough{\lstinline!remote!}\gls{pc} \passthrough{\lstinline!\#2!}
can acces the proxy running on \passthrough{\lstinline!remote!}\gls{pc}
\passthrough{\lstinline!\#1!}.

@@

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality \cite{PTPIEEE1588} can be used on
many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module!}.

@@

\hypertarget{merging-the-sensor-capabilities}{%
\subsubsection{Merging the Sensor
Capabilities}\label{merging-the-sensor-capabilities}}

@@

When using sensors with different capabilites, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \passthrough{\lstinline!info!}
command of each sensor is queried. This information is added to the
previously created \gls{lut}. Duplicate entries are summarised (see
Table \ref{Sensor_capabilities_merging_algorithm.csv}) and returned to
the host when the \passthrough{\lstinline!info!} \ref{lst:mtsc} command
is received over network.

@@

\hypertarget{dynamic-extension-of-the-available-network-proxy-commands}{%
\subsubsection{Dynamic extension of the available Network-Proxy
Commands}\label{dynamic-extension-of-the-available-network-proxy-commands}}

@@

For commands where there are several entries for
\passthrough{\lstinline!CAPABLE SENSORS ID LUT!}
\ref{Sensor_capabilities_merging_algorithm.csv}, there are two possible
approaches to how the command is processed:

@@

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!readsensor <axis> <sensor number>!}
  -\textgreater{} \passthrough{\lstinline!readsensor <axis> <ID>!}
\item
  \passthrough{\lstinline!opmode!}-\textgreater{}
  \passthrough{\lstinline!opmode <ID>!}
\end{itemize}

@@

\begin{lstlisting}[language=Python, caption={MRPHal example to use an connected hardware sensor to store readings inside of a measurement}, label=lst:mrpexample_hal]
from MRP import MRPHalSerialPortInformation, MRPHal, MRPBaseSensor, MRPReadingSource
# SEARCH FOR CONNECTED SENSORS
## LISTS LOCAL CONNECTED OR NETWORK SENSORS
system_ports = MRPHalSerialPortInformation.list_sensors()
sensor = MRPHal(system_ports[0])
# OR USE SPECIFIED SENSOR DEVICE
device_path = MRPHalSerialPortInformation("UNFSensor1")
sensor = MRPHal(device_path)
# RAW SENSOR INTERACTION MODE
sensor.connect()
basesensor = MRPBaseSensor.MRPBaseSensor(sensor)
basesensor.query_readout()
print(basesensor.get_b()) # GET RAW MEASUREMENT
print(basesensor.get_b(1)) # GET RAW DATA FROM SENSOR WITH ID 1
# TO GENERATE A READING THE perform_measurement FUNCTION CAN BE USED
reading_source = MRPReadingSourceHelper.createReadingSourceInstance(sensor)
result_readings: [MRPReading] = reading_source.perform_measurement(_readings=1, _hwavg=1)
\end{lstlisting}

@@

This final example shows the use of the
\passthrough{\lstinline!MRPVisualisation!} module, which provides
general functions for visualising measurements. The visualisation
optionsmakes it possible to visually assess the results of a
measurement. This is particularly helpful for full-sphere measurements
recorded with the \passthrough{\lstinline!3D: Fullsphere!}
\ref{d-fullsphere} sensor. The sub-module
\passthrough{\lstinline!MRPPolarVisualisation!} is specially designed
for these. The figure
\ref{Example_full_sphere_plot_of_an_measurement_using_the_MRPVisualisation_module.png}
shows a plot of a fullsphere measurement. It is also possible to export
the data from the \passthrough{\lstinline!MRPAnalysis!} module
graphically as diagrams. The \passthrough{\lstinline!MRPVisualisation!}
modules are used here. The following example
\ref{lst:mrpexample_visualisation} shows the usage of both modules.

\begin{lstlisting}[language=Python, caption={MRPVisualisation example which plots a fullsphere to an image file}, label=lst:mrpexample_visualisation]
from MRP import MRPPolarVisualization
# CREATE MRPPolarVisualization INSTANCE
## IT CAN BE REUSED CALLING plot2d AGAIN, AFTER LINKED READING DATA WERE MODIFIED
visu = MRPPolarVisualization.MRPPolarVisualization(reading)
# 2D PLOT INTO A WINDOW
visu.plot2d_top(None)
visu.plot2d_side(None)
# 3D PLOT TO FILE
visu.plot3d(os.path.join('./plot3d_3d.png'))
# PLOT ANALYSIS RESULTS
from MRP import MRPDataVisualization
MRPDataVisualization.MRPDataVisualization.plot_error([reading_a, reading_b, reading_c])
\end{lstlisting}

@@

@@

The following example code \ref{lst:mrpexample_hallbach}, shows how a
simple Hallbach magnetic ring can be generated.

This can then be used to construct a Halbach ring magnet (see chapter
\ref{magnet-system}) for a low-field \gls{mri}.

@@

In the last step, a 3D model with the dimensions of the magnet type set
is generated from the generated magnet positions. The result is an
\passthrough{\lstinline!OpenSCAD!} \cite{OpenSCAD} file, which
contains the module generated. After computing the model using the
\passthrough{\lstinline!OpenSCAD!} \gls{cli} utility, the following
model rendering
\ref{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
can be generated.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}
\caption{Generated Hallbach array with generated cutouts for eight
magnets
\label{Generated_Hallbach_array_with_generated_cutouts_for_eight_magnets.png}}
\end{figure}

\hypertarget{usability-improvements}{%
\chapter{Usability Improvements}\label{usability-improvements}}

@@

\begin{itemize}
\tightlist
\item
  Detection of connected sensors
\item
  Configuration of measurement series
\item
  Recording of measured values from stored measurement series
\item
  Simple commands for checking recorded measurement series and their
  data
\end{itemize}

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is an exported file with the measured
values. These can then be read in again using the
\passthrough{\lstinline!MRPReading!} module and processed further. The
following bash code \ref{lst:mrpcli_config_run} shows the setup
procedure in detail:

@@

\hypertarget{programmable-data-processing-pipeline}{%
\section{Programmable Data Processing
Pipeline}\label{programmable-data-processing-pipeline}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Import the measurements
\item
  Determine sensor bias value from imported measurements using a
  reference measurement
\item
  Apply linear temperature compensation
\item
  Export the modified measurements
\item
  Create a graphical plot of all measurements with standard deviation
\end{enumerate}

@@

Each pipeline step is divided into \passthrough{\lstinline!stages!},
which contain a name, the function to be executed and its parameters.

\newpage

The various steps are then linked by using the
\passthrough{\lstinline!stage <name>!} makro as input parameter of the
next function to be executed (see comments in
\ref{lst:mrpuddp_example_yaml}).
